Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-03 paper/paper.tex
Added loans experiment
Added TODOs

@@

@@

A \emph{row} $r_i$ is a lookup table or dictionary. A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows. The set of all databases is denoted $\dbs$. The attributes of a $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$. The domain of $A_i$ is $\Omega_i$.

@@

@@

@@

@@

@@

As for privacy, on the other hand, it introduces risks of information leakage. Storage of real data may inadvertently reveal sensitive information by data inference attacks. Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.

@@

Underneath the hood, the tool employs a Markov random field. The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to inference from the fitted Markov random field.

@@

@@

@@

% TODO: mention model fit time?

\subsection{Accuracy}

@@

\subsection{Impossibility}

@@

>>>>

TODO: add more connections to our work

@@

TODO: some works aim to change properties of og data. we want to preserve. so we dont consider this case

@@

TODO: Let $r_i$ denote a \emph{row} $r_i$ is a function. A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows. The set of all databases is denoted $\dbs$. The attributes of a $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$. The domain of $A_i$ is $\Omega_i$.

@@

TODO: cite elements of info theory

@@

TODO: let Y be binary

@@

TODO: mention in results we only tested binary predictions

@@

TODO: N is multivariate normal distribution and sigma and identity function. I sub p

TODO: Da needs to take distributions. change symbols. lowercase phi

@@

As for privacy, on the other hand, it introduces risks of information leakage. Releasings of real data may inadvertently reveal sensitive information by data inference attacks.

TODO: ppl may infer info from auditors analyses Releasings. repeated queries

Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.

@@

Underneath the hood, the tool employs a Markov random field. The select step corresponds to marking cliques in a Markov random field, and the generate step corresponds to sampling by inference from the fitted Markov random field.

@@

TODO: mst was obtained. delete the word algorithm

@@

TODO: use latex algorithm. pseudo code

@@

% TODO: mention model fit time? yes. do experiments!

TODO: \subsection{Positive Results}

@@

TODO: \subsection{Negative Results}

@@

TODO: expand all defs and count the nums of avail vars
